---
title: "Figure Generation for Normalization Paper"
author: "Antony Sikorski"
output: pdf_document
---

Make sure to set correct working directory in this block:  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#make sure to set correct working directory
knitr::opts_knit$set(root.dir = normalizePath("C:/Users/anton/Desktop/Normalization_Paper_Github/Normalization-Paper")) #CHANGE THIS
```

### Local LatticeKrig Install (Research Version)

```{r}
#local development install
#install temporary version of LatticeKrig

#UNCOMMENT THIS LINE IF YOU HAVE NOT INSTALLED RESEARCH VERSION YET
#install.packages("LatticeKrigRPackage/LatticeKrig", repos = NULL, type="source")

#IF YOU WOULD LIKE TO REINSTALL CRAN (default) LATTICEKRIG
#remove.packages("LatticeKrig")
#install.packages("LatticeKrig")
```

### Necessary Libraries and Source Functions:  

```{r}
library(LatticeKrig)

#install if you haven't already 
library(ggplot2)
library(scales)
library(dplyr)
library(tidyr)
library(patchwork)
library(spam64)
library(fields)
library(reshape2)
library(scico)
library(fftwtools)

#convenient functions
source("latticekrig_functions/fillGrid.R")
```


### One Dimensional Artifact Figure (Section 1)

```{r}
set.panel(1,1)
n<- 20
x<-  cbind(seq( 0,1 , length.out= n))
set.seed(121)
y<- 10*x*(1-x) + .2*rnorm( n)

xGrid<- cbind( seq( 0,1,length.out= 200))

NC<- 8
a.wght<- 2.001
obj<- LatticeKrig( x, y, NC=NC, a.wght=a.wght, nlevel=1,
                  normalize=TRUE)
gHat<- predict( obj,xGrid )
obj1<- LatticeKrig( x, y, NC=NC,  a.wght=a.wght,
                   normalize=FALSE,nlevel=1,)
gHat1<- predict( obj1,xGrid )

#ggplot option
# Convert data to data frames for ggplot
df_points <- data.frame(x = x, y = y)
df_predictions <- data.frame(xGrid = xGrid,
                             Unnormalized = gHat1,
                             Normalized = gHat)
df_differences <- data.frame(xGrid = xGrid[-1], 
                             Unnormalized = diff(gHat1),
                             Normalized = diff(gHat))
                             


# Plotting
plot1 <- ggplot() +
  geom_point(data = df_points, aes(x = x, y = y), shape = 16) +
  geom_line(data = df_predictions, 
            aes(x = xGrid, y = Normalized, colour = "Normalized"), 
            size = 1.3, alpha = 0.7) +
  geom_line(data = df_predictions, 
            aes(x = xGrid, y = Unnormalized, colour = "Unnormalized"),
            size = 1.2, alpha = 0.7) +
  labs(colour = "Fit", x = "s", y = expression(f(s))) +
  scale_colour_manual(values = c("Normalized" = "#1093ff", 
                                 "Unnormalized" = "#f00036")) +
  theme_minimal()

plot2 <- ggplot() +
  geom_line(data = df_differences, 
            aes(x = xGrid, y = Normalized, colour = "Normalized"),
            size = 1.3, alpha = 0.7) +
  geom_line(data = df_differences, 
            aes(x = xGrid, y = Unnormalized, colour = "Unnormalized"),
            size = 1.2, alpha = 0.7) +
  labs(colour = "Fit", x = "s", y = expression(f(s[i+1]) - f(s[i]))) +
  scale_colour_manual(values = c("Normalized" = "#1093ff", 
                                 "Unnormalized" = "#f00036")) +
  theme_minimal()

# Combine plots side by side using patchwork
combined_plot <- plot1 + plot2 + plot_layout(ncol = 2) + 
  plot_layout(guides = 'collect', axis_titles = 'collect')
combined_plot

# pdf("timing_error/figures/1d_artifacts.pdf",
#     width = 8, height = 2.8)
# combined_plot
# dev.off()
```

### Basis Function Matrix Sparsity and Variance Uniformity (Section 2)

```{r}
wendland <- function(x, c, overlap) {
  # adjust s for overlap
  s <- abs(x - c) / overlap
  phi <- ifelse(s <= 1, ((1 - s)^6) * (35 * s^2 + 18 * s + 3) / 3, 0)
  return(phi)
}

plot_cartoon_sum <- function(overlap) {
  centers <- c(1, 3, 5, 7, 9)
  x_range_full <- seq(0, 10, by = 0.01)
  sum_phi_full <- numeric(length(x_range_full))
  data_list <- list()
  
  for (c in centers) {
    x_range_compact <- seq(max(0, c - overlap), min(10, c + overlap), by = 0.01)
    phi_values_compact <- sapply(x_range_compact, wendland, c = c, overlap = overlap)
    data_list[[as.character(c)]] <- data.frame(x = x_range_compact, y = phi_values_compact, center = c)
  }
  
  full_data <- do.call(rbind, data_list)
  full_data$center <- factor(full_data$center)
  
  p1 <- ggplot(full_data, aes(x = x, y = y, color = center)) +
    geom_line(size = 1.3) +
    geom_point(data = data.frame(x = seq(0, 10, by = 0.5), y = rep(0, length(seq(0, 10, by = 0.5)))), aes(x = x, y = y), color = "black", size = 2) +
    scale_color_grey(start = 0, end = 0.8) +
    labs(x = "s", y = expression(phi(s))) +
    theme_minimal() +
    ylim(c(0, 1.4))
  
  # Adding sum
  for (i in seq_along(x_range_full)) {
    for (c in centers) {
      sum_phi_full[i] <- sum_phi_full[i] + wendland(x_range_full[i], c, overlap)^2
    }
  }
  
  sum_data <- data.frame(x = x_range_full, y = sum_phi_full)
  p1 <- p1 + geom_line(data = sum_data, aes(x = x, y = y), color = "magenta", linetype = "dotdash", size = 1.3) + #theme(text = element_text(size = 15), # Increase base text size
 #         axis.title = element_text(size = 15), # Customize axis titles
  #        axis.text = element_text(size = 11), # Customize axis text
   #       legend.title = element_text(size = 11), # Customize legend title
    #      legend.text = element_text(size = 11)) + 
    scale_x_continuous(breaks = c(1, 3, 5, 7, 9), labels = c("1", "3", "5", "7", "9"))
  
  # Matrix plot
  evaluation_points <- seq(0, 10, by = 0.5)
  basis_function_matrix <- matrix(nrow = length(evaluation_points), ncol = length(centers))
  
  for (i in 1:length(evaluation_points)) {
    for (j in 1:length(centers)) {
      basis_function_matrix[i, j] <- wendland(evaluation_points[i], centers[j], overlap)
    }
  }
  
  basis_function_matrix <- t(basis_function_matrix[nrow(basis_function_matrix):1, ])
  mat_melted <- melt(basis_function_matrix)
  mat_melted <- transform(mat_melted, Var1 = as.numeric(as.character(Var1)), Var2 = as.numeric(as.character(Var2)))
  p2 <- ggplot(mat_melted, aes(x = Var1, y = Var2, fill = value)) +
    geom_tile() +
    scale_fill_viridis_c() +
    labs(x = expression(paste("Center of ", phi(s))), y = "Points Evaluated") +
    theme_minimal() + 
    scale_x_continuous(breaks = c(1, 2, 3, 4, 5), labels = c("1", "3", "5", "7", "9")) #+ 
    # theme(text = element_text(size = 15), # Increase base text size
    #       axis.title = element_text(size = 15), # Customize axis titles
    #       axis.text = element_text(size = 11), # Customize axis text
    #       legend.title = element_text(size = 11), # Customize legend title
    #       legend.text = element_text(size = 11))
  
  return(list(p1 = p1, p2 = p2))
}

# usage
plots <- plot_cartoon_sum(overlap = 6)
basis_plot <- plots$basis_function_plot
matrix_plot <- plots$matrix_plot



overlap_plots <- plot_cartoon_sum(overlap = 6)
basis_overlap <- overlap_plots$p1
mat_overlap <- overlap_plots$p2


sparse_plots <- plot_cartoon_sum(overlap = 2)
basis_sparse <- sparse_plots$p1
mat_sparse <- sparse_plots$p2

basis_sparsity_fig <- basis_overlap + basis_sparse + mat_overlap + mat_sparse + 
  plot_layout(guides = 'collect', axis_titles = 'collect')
plot(basis_sparsity_fig)

pdf("timing_error/figures/overlap_sparsity_pink1.pdf", width = 8, height = 5)
plot(basis_sparsity_fig)
dev.off()
```


### FFT Process Visualization Figure (Section 3)

```{r}
fftSmoother <- function(LKinfo, sGrid, nr, nc, plots = FALSE, col = turbo(512), fftcol = turbo(512)){
  
  #fft step and dimensions
  roughMat <- as.surface(sGrid, LKrig.cov(sGrid, LKinfo = LKinfo, marginal=TRUE ))[["z"]]
  fftStep <- fftw2d((roughMat)/length(roughMat))
  snr <- nrow(fftStep)
  snc <- ncol(fftStep)
  
  #instantiate empty matrix
  temp <- matrix(0, nrow = nr, ncol = nc)
  
  # Helpful for indexing later 
  bigindY <- 1:ceiling(snr/2) #1:3
  bigindX <- 1:ceiling(snc/2) #1;3
  indY <- 1:floor(snr/2) #1;2
  indX <- 1:floor(snc/2) #1:2
  bigOffsetY <- (nr - floor(snr/2)) 
  bigOffsetX <- (nc - floor(snc/2))
  smallOffsetY <- (snr - floor(snr/2)) 
  smallOffsetX <- (snc - floor(snc/2))
  
  # Stuffing the small FFT result into the large matrix of zeroes 
  temp[bigindY, bigindX] <- fftStep[bigindY, bigindX] #top left corner (actually bottom left)
  temp[bigindY, (indX + bigOffsetX)] <- fftStep[bigindY, (indX + smallOffsetX)] #top right corner
  temp[(indY + bigOffsetY), bigindX] <- fftStep[(indY + smallOffsetY), bigindX] #bottom left corner 
  temp[(indY + bigOffsetY), (indX + bigOffsetX)] <- fftStep[(indY + smallOffsetY), (indX + smallOffsetX)] #bottom right corner
    
  
  #takes the inverse of the modified big matrix to return a smoothed version of the input matrix
  smoothMat <- Re(fftw2d(temp, inverse = 1))

  #shifting
  yShift <- floor((nr/snr)/2)
  xShift <- floor((nc/snc)/2)
  
  smoothMat <- LKrig.shift.matrix(smoothMat, 
                                  shift.row = yShift, 
                                  shift.col = xShift, periodic = c(TRUE, TRUE))
  
  #getting basis centers
  basisNodes<- make.surface.grid(
  LKinfo$latticeInfo$grid[[1]]
  )
  basisNodes1 <- LKrigLatticeCenters(LKinfo, 1)
  basisNodes2 <- make.surface.grid(basisNodes1)

  
  if (plots == TRUE){
    
    #plotting params
    #par(mfrow = c(2,2))
    
    #capture the axis of the original grid (the -1 to 1 part) (take from the object)
    xboundLeft <- as.numeric(LKinfo$x[1,1])
    xboundRight <- as.numeric(LKinfo$x[2,1])
    yBoundLow <- as.numeric(LKinfo$x[1,2])
    yBoundHigh <- as.numeric(LKinfo$x[2,2])
    
    smallXaxis <- seq(xboundLeft,xboundRight, length.out = snc)
    smallYaxis <- seq(yBoundLow,yBoundHigh, length.out = snr)
    bigXaxis <- seq(xboundLeft,xboundRight, length.out = nc)
    bisYaxis <- seq(yBoundLow,yBoundHigh, length.out = nr)
    
    #bounds for fft plots
    fftmin <- min(log(Mod(temp) + 0.00001))
    fftmax <- max(log(Mod(fftStep) + 0.00001))
    
    #bounds for regular plots
    colmin <- min(smoothMat)
    colmax <- max(smoothMat)
    
    
    #plotting the original coarse matrix
    imagePlot(smallXaxis, smallYaxis, roughMat, col = col, zlim = c(colmin, colmax), 
              xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")#, horizontal = TRUE)
    box(lwd = 1.5, col = "black")
    points(basisNodes2, pch = 21, cex = 1.8, col = "black", bg = "ivory", lwd = 2)
    
    
    #plotting the small fft step, 0.00001 necessary as log(0) will not plot
    imagePlot(smallXaxis, smallYaxis, log(Mod(fftStep) + 0.00001), col = fftcol, 
              zlim = c(fftmin, fftmax), xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
    box(lwd = 1.5, col = "black")
    
    #plotting the large fft padding step 
    imagePlot(bigXaxis, bisYaxis, log(Mod(temp) + 0.00001), col = fftcol, 
              zlim = c(fftmin, fftmax), xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
    box(lwd = 1.5, col = "black")
    
    
    #plotting the fine matrix after inverse fft 
    imagePlot(bigXaxis, bisYaxis, smoothMat, col = col, zlim = c(colmin, colmax), 
              xaxt = 'n', yaxt = 'n', xlab = "", ylab = "")
    box(lwd = 1.5, col = "black")
    points(basisNodes2, pch = 21, cex = 1.2, col = "black", bg = "ivory", lwd = 2)
    
    #plotting params
    par(mfrow = c(1,1))
    
    #print(colmin)
    #print(colmax)
    
  }
  
  return(smoothMat)
}

my_mako <- mako(256)
my_mako[256] <- "#FFFFFFFF"
my_mako <- rev(my_mako)



proveItWorks <- function(ORIGINALGRID, BIGGRID){
  # create a simple 1 level model
  xr<- c( -1,1)
  yr<- c( -1,1)
  LKinfo<- LKrigSetup(cbind(xr, yr), nlevel=1, NC=5, NC.buffer = 4, 
                      a.wght= 4.05, normalize= FALSE)
  
  #calculating initial coarse grid
  gridList<- list( x= seq( -1,1,length.out= ORIGINALGRID),
                   y= seq( -1,1,length.out= ORIGINALGRID) )
  sGrid<- make.surface.grid(gridList)
  look<- LKrig.cov(sGrid, LKinfo = LKinfo, marginal=TRUE )
  
  #performing fft normalization
  #first 4 plots generated here
  tester <- fftSmoother(LKinfo, sGrid, nr = BIGGRID, nc = BIGGRID, plots = TRUE, 
                        col = plasma(256),
                        fftcol = my_mako)

  
  #calculting true fine grid
  gridList1 <- list( x= seq( -1,1,length.out=BIGGRID),
                   y= seq( -1,1,length.out=BIGGRID) )
  
  sGrid1 <- make.surface.grid(gridList1)
  look1 <- LKrig.cov(sGrid1, LKinfo = LKinfo, marginal=TRUE )
  
  #plotting the big original matrix 
  #last plot
  basisNodes<- make.surface.grid(
  LKinfo$latticeInfo$grid[[1]]
  )
  basisNodes1 <- LKrigLatticeCenters(LKinfo, 1)
  basisNodes2 <- make.surface.grid(basisNodes1)
  imagePlot( as.surface(sGrid1, look1), col = plasma(256), 
             xaxt = 'n', yaxt = 'n')#, zlim = c(4.411986, 5.129177))
  box(lwd = 1.5, col = "black")
  points(basisNodes2, pch = 21, cex = 1.2, col = "black", bg = "ivory", lwd = 2)
  
}


proveItWorks(13, 31)
```


### Timing and Error Results (Section 4)

Loading the dataframe: 

```{r}
load("timing_error/dataframes/normalization_times_error.rda")
df <- df[order(df$NumBasis, df$Size),]
print(df)
```

We compute the median of five training runs, and then use that median data set for the following plots:  

```{r}
# reshape the data to a long format
data_long <- reshape(df, 
                     varying = list(c("None", "Exact", "Kronecker", "FFT")), 
                     v.names = "Time",
                     timevar = "Method",
                     times = c("None", "Exact", "Kronecker", "FFT"),
                     direction = "long")

# filter and plot for each unique 'NumBasis' value
unique_basis_nums <- unique(data_long$NumBasis)

#data long median calculation
data_long_median <- data_long %>%
  group_by(Size, NumBasis, Method) %>%
  summarise(MedianTime = median(Time),
            MaxTime = max(Time),
            MinTime = min(Time),
            MeanErrorPercent = first(`Mean % Error`),
            MaxErrorPercent = first(`Max % Error`),
            Method = first(Method),
            .groups = 'drop')

```

Timing plot: 

```{r}
unique_basis_nums_no15 <- unique_basis_nums[2:5]

custom_colors <- c("orange2", "cyan3","deeppink2" ,"darkorchid4")

side_lengths <- c(500, 750, 1000, 1250, 1500, 2000)
squared_lengths <- side_lengths^2
side_lengths <- c("500", "750", "1000", "1250", "1500", "2000")


data_filtered_25 <- filter(data_long_median, NumBasis == 25)

  
p1 <- ggplot(data_filtered_25, aes(x = Size^2, y = MedianTime, colour = Method, fill = Method)) +
    geom_ribbon(aes(ymin = MinTime, ymax = MaxTime), alpha = 0.3, color = NA) +
    geom_line(linetype = "dotted") +
    geom_point(size = 2.6, shape = 18) +
    scale_y_log10(limits = c(1,2200)) + 
    scale_x_log10(labels =side_lengths, breaks = squared_lengths) +
    #scale_x_log10(labels = function(x) format(x, scientific = TRUE), breaks = c(250000, 1000000, 4000000)) +
    annotation_logticks(sides = "l", outside = TRUE, color = "darkgrey") +
    coord_cartesian(clip = "off") +
    theme_minimal() +
    labs(x = "n", y = "Time (s)") + 
    theme(panel.border = element_rect(color = "grey", fill = NA, size = 0.5),
          axis.title.y = element_text(margin = margin(r = 10, unit = "pt")),
          axis.title.x = element_text(margin = margin(t = 10, unit = "pt")),
          axis.text.y = element_text(margin = margin(r = 10, unit = "pt")), 
          axis.text.x = element_blank()) +  # Adjust right margin for y-axis title
    scale_color_manual(values = custom_colors) +
    scale_fill_manual(values = custom_colors)

#plot(p1)


data_filtered_35 <- filter(data_long_median, NumBasis == 35)

  
p2 <- ggplot(data_filtered_35, aes(x = Size^2, y = MedianTime, colour = Method, fill = Method)) + 
    geom_ribbon(aes(ymin = MinTime, ymax = MaxTime), alpha = 0.3, color = NA) +
    geom_line(linetype = "dotted") +
    geom_point(size = 2.6, shape = 18) +
    scale_y_log10(limits = c(1,2200)) + 
    scale_x_log10(labels =side_lengths, breaks = squared_lengths) +
    #scale_x_log10(labels = function(x) format(x, scientific = TRUE), breaks = c(250000, 1000000, 4000000)) +
    #annotation_logticks(sides = "l", outside = TRUE, color = "darkgrey") +
    coord_cartesian(clip = "off") +
    theme_minimal() +
    labs(x = "n", 
         y = "Time (s)") + 
    theme(panel.border = element_rect(color = "grey", fill = NA, size = 0.5),
          axis.title.y = element_text(margin = margin(r = 10, unit = "pt")),
          axis.title.x = element_text(margin = margin(t = 10, unit = "pt")),
          axis.text.y = element_blank(), 
          axis.text.x = element_blank()) + 
  scale_color_manual(values = custom_colors) +  # Apply custom colors to lines
    scale_fill_manual(values = custom_colors)
  
#plot(p2)


data_filtered_50 <- filter(data_long_median, NumBasis == 50)

  
p3 <- ggplot(data_filtered_50, aes(x = Size^2, y = MedianTime, colour = Method, fill = Method)) + 
    geom_ribbon(aes(ymin = MinTime, ymax = MaxTime), alpha = 0.3, color = NA) +
    geom_line(linetype = "dotted") +
    geom_point(size = 2.6, shape = 18) +
    scale_y_log10(limits = c(1,2200)) + 
    scale_x_log10(labels =side_lengths, breaks = squared_lengths) +
    #scale_x_log10(labels = function(x) format(x, scientific = TRUE), breaks = c(250000, 1000000, 4000000)) +
    annotation_logticks(sides = "l", outside = TRUE, color = "darkgrey") +
    coord_cartesian(clip = "off") +
    theme_minimal() +
    labs(x = "n", 
         y = "Time (s)") + 
    theme(panel.border = element_rect(color = "grey", fill = NA, size = 0.5),
          axis.title.y = element_text(margin = margin(r = 10, unit = "pt")),
          axis.title.x = element_text(margin = margin(t = 10, unit = "pt")),
          axis.text.y = element_text(margin = margin(r = 10, unit = "pt"))) + #axis.text.x = element_text(angle = -30, hjust = 0)
  scale_color_manual(values = custom_colors) +  # Apply custom colors to lines
    scale_fill_manual(values = custom_colors)
  
#plot(p3)



data_filtered_100 <- filter(data_long_median, NumBasis == 100)


p4 <- ggplot(data_filtered_100, aes(x = Size^2, y = MedianTime, colour = Method, fill = Method)) + 
    geom_ribbon(aes(ymin = MinTime, ymax = MaxTime), alpha = 0.3, color = NA) +
    geom_line(linetype = "dotted") +
    geom_point(size = 2.6, shape = 18) +
    scale_y_log10(limits = c(1,2200)) + 
    scale_x_log10(labels =side_lengths, breaks = squared_lengths) +
    #scale_x_log10(labels = function(x) format(x, scientific = TRUE), breaks = c(250000, 1000000, 4000000)) +
    #annotation_logticks(sides = "l", outside = TRUE, color = "darkgrey") +
    coord_cartesian(clip = "off") +
    theme_minimal() +
    labs(x = "n", 
         y = "Time (s)") + 
    theme(panel.border = element_rect(color = "grey", fill = NA, size = 0.5),
          axis.title.y = element_text(margin = margin(r = 10, unit = "pt")),
          axis.title.x = element_text(margin = margin(t = 10, unit = "pt")),
          axis.text.y = element_blank()) + #axis.text.x = element_text(angle = -30, hjust = 0)
  scale_color_manual(values = custom_colors) +  # Apply custom colors to lines
    scale_fill_manual(values = custom_colors)
  
#plot(p4)

all_timing_1 <- p1 + p2 + p3 + p4 + 
  plot_layout(guides = 'collect', axis_titles = 'collect')
plot(all_timing_1)

pdf("timing_error/figures/timing_all_fish.pdf", width = 8, height = 5)
plot(all_timing_1)
dev.off()

```



We are also interested in the error. Both maximum and mean error are recorded for each run (they will be the exact same each time for the same number of basis functions and coarse grid size):


```{r}
names(data_long_median)[names(data_long_median) == "MeanErrorPercent"] <- "Mean"
names(data_long_median)[names(data_long_median) == "MaxErrorPercent"] <- "Max"
#data_long_error <- data_long_median %>% group_by(`Mean Error`, `Max Error`)
data_long_error <- data_long_median[data_long_median$Method == "FFT",]
```


```{r}
# interesed in magnitude
data_long_error$Mean <- abs(data_long_error$Mean)

# transform data to a long format for easier plotting with ggplot2
data_long_error <- data_long_error %>%
  dplyr::select(Size, NumBasis, Mean, Max) %>%
  tidyr::pivot_longer(cols = c(Mean, Max),
                      names_to = "ErrorType",
                      values_to = "ErrorValue")

#dont need the 15, paper uses 35 and up 
data_long_error_no15 <- data_long_error %>% filter(NumBasis != 15)

custom_colors <- c("orange2", "deeppink2", "cyan3", "darkorchid4")


# plot for paper
error_all_bfuncs <- ggplot(data_long_error_no15, aes(x = Size^2, 
                                  y = ErrorValue, 
                                  color = as.factor(NumBasis), 
                                  shape = ErrorType, # Add shape aesthetic for ErrorType
                                  group = interaction(NumBasis, ErrorType))) +
  geom_point(size = 4, alpha = 0.6) +
  scale_y_log10() + 
  scale_x_log10(labels =side_lengths, breaks = squared_lengths) +
  #scale_x_log10(labels = function(x) format(x, scientific = FALSE), breaks = c(250000, 1000000, 4000000)) +
  annotation_logticks(sides = "l", outside = TRUE, color = "darkgrey") +
  coord_cartesian(clip = "off") +
  scale_shape_manual(values = c("Mean" = 19, "Max" = 17)) +
  scale_color_manual(values = custom_colors, name = "NumBasis") + # Apply custom colors
  labs(x = "n",
       y = "Error (%)",
       color = "NumBasis",
       shape = "Error Type") +
  theme_minimal() +
    theme(panel.border = element_rect(color = "grey", fill = NA, size = 0.5),
          axis.title.y = element_text(margin = margin(r = 10, unit = "pt"), size = 9),
          axis.title.x = element_text(margin = margin(t = 6, unit = "pt"), size = 9),
          axis.text.y = element_text(margin = margin(r = 10, unit = "pt"), size = 7),
          axis.text.x = element_text(size = 7),
          legend.text = element_text(size = 8), 
          legend.title = element_text(size = 9)) +
  guides(col = guide_legend(title = "     r"),
         shape = guide_legend(title = "Error Type"))

plot(error_all_bfuncs)

pdf("timing_error/figures/Error_allBfuncs.pdf", width = 6, height = 3.2)
plot(error_all_bfuncs)
dev.off()
```


### Other Sources of Error (Section 4.3)

Here we test a few theories. None of these plots will be used in the paper for pretty visualizations. They are just for investigation and understanding.  

For example, how does coarse grid size impact the error: 

```{r}
load("timing_error/dataframes/coarsegrid_error.rda")
print(df_CoarseGrid)
print.data.frame(df_CoarseGrid)

plot(df_CoarseGrid$`Coarse Grid`, df_CoarseGrid$MaxErrorPercent, pch = 16, 
     xlab = "Starting Grid Side Length", ylab = "Mean Error (%)")
lines(df_CoarseGrid$`Coarse Grid`, df_CoarseGrid$MaxErrorPercent, 
      col = "blue", lwd = 1.5)


plot(df_CoarseGrid$`Coarse Grid`, df_CoarseGrid$MeanErrorPercent, pch = 16, 
     xlab = "Starting Grid Side Length", ylab = "Max Error (%)")
lines(df_CoarseGrid$`Coarse Grid`, df_CoarseGrid$MeanErrorPercent, pch = 16, 
      col = "blue", lwd = 1.5)
```

Course grid increase will monotonically decrease the error until we end up with machine error. 


How does the number of buffer function impact the error? 

```{r}
load("timing_error/dataframes/buffer_error.rda")
print.data.frame(df_Buffer)

plot(df_Buffer$NumBuffer, df_Buffer$MaxErrorPercent, pch = 16, 
     xlab = "Buffer Functions (NC)", ylab = "Mean Error (%)")
lines(df_Buffer$NumBuffer, df_Buffer$MaxErrorPercent, 
      col = "red", lwd = 1.5)


plot(df_Buffer$NumBuffer, abs(df_Buffer$MeanErrorPercent), pch = 16, 
     xlab = "Buffer Functions (NC)", ylab = "Max Error (%)")
lines(df_Buffer$NumBuffer, abs(df_Buffer$MeanErrorPercent), pch = 16, 
      col = "red", lwd = 1.5)
```

Appears to have a minimum at 10 buffer functions. 

How does the awght (overlap) impact the error? 

```{r}
load("timing_error/dataframes/awght_error.rda")
print.data.frame(df_awght)

plot(df_awght$A.wght, df_awght$MaxErrorPercent, pch = 16, 
     xlab = "awght param", ylab = "Mean Error (%)")
lines(df_awght$A.wght, df_awght$MaxErrorPercent, 
      col = "darkgreen", lwd = 1.5)


plot(df_awght$A.wght, abs(df_awght$MeanErrorPercent), pch = 16, 
     xlab = "awght param", ylab = "Max Error (%)")
lines(df_awght$A.wght, abs(df_awght$MeanErrorPercent), pch = 16, 
      col = "darkgreen", lwd = 1.5)
```

It appears that the awght (overlap) slightly impacts the error, and the original 4.05 parameter works the best as expected. 