---
title: "Simulated Experiments: Fitting and Predicting"
author: "Antony Sikorski"
output: html_document
---

Make sure to set correct working directory in this block: 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#make sure to set correct working directory
knitr::opts_knit$set(root.dir = normalizePath("C:/Users/anton/Desktop/Normalization_Paper_Github/Normalization-Paper"))
```


Uncomment to install LatticeKrig: 
```{r}
# install.packages("LatticeKrig")
```

Loading necessary libraries and files: 

```{r}
library(fields)
library(hdf5r)
library(LatticeKrig)
library(tictoc)
library(fftwtools)
library(ggplot2)
library(ggpubr)
library(xtable)
library(gridExtra)
library(spam64)
library(viridis)
library(maps)

# parallel conditional sim 
source("latticekrig_functions/LKrig.sim.conditional.foreach.R")

source("latticekrig_functions/LKrigNormalizeBasisFFTInterpolate_scale.R")

#convenient grid checker
source("latticekrig_functions/fillGrid.R")
```

Setup for the whole experiment: 

```{r}
# these are universal and very important
dataCase <- "MAR" #options are MAR, BLOCKS 
normalizeCase <- "none" #options are fft, kronecker, exact, none

#decides if we do conditional sim or not 
conditionalSim <- FALSE
#number of draws
numDraws <- 10
```

Making the full dataset with fast option in fields: 

```{r}
tic()
#creating data
set.seed(236)

#nested, 48r - 48 + 1 = data
smolGrid <- list( x = c(1:25), y = c(1:25))
check <- fillGrid(smolGrid, 48)

grid<- list( x= seq( from = 0, to = 90,length.out = 1153), 
               y= seq( from = 0, to = 90,length.out = 1153)) 

#sanity check
test.for.zero(length(check$x), length(grid$x))
test.for.zero(length(check$y), length(grid$y))

obj<- circulantEmbeddingSetup( grid,
                               cov.args = list( 
                                 Covariance="Matern", 
                                 aRange=6, 
                                 smoothness=1.0
                                 )
                              )

field <- circulantEmbedding(obj)
toc()
field <- 5 * field + 2 + (0.2*rnorm(length(field)))

imagePlot(field, main = "Simulated Random Field with Matern Covariance", 
          col = turbo(256))
  
coords <- expand.grid(lat = grid$x, lon = grid$y)
air_temp <- as.vector(field)

df <- data.frame(lat = coords$lat, lon = coords$lon, air_temp = air_temp)
save(df, file = "big_data_analysis/dataframes/simulatedFull.rda")
```

Creating training and test data for both cases: 

```{r}

if (dataCase == "MAR"){

  #creating train and test sets
  missingness <- 0.8
  
  set.seed(777)
  n <- nrow(df)
  ind <- sample(1:n, size = round(missingness * n), replace = FALSE)
  
  train <- df[-ind, ]
  test <- df[ind, ]
  
  #sanity check to make sure i still have the same size grid
  print(length(unique(train[,1])))
  print(length(unique(train[,2])))
  print(length(unique(df[,1])))
  print(length(unique(df[,2])))
  
  
  #full data visual
  fullPlot <- ggplot(df) + geom_raster(aes(x = lon, y = lat, fill = air_temp)) +
    theme_bw() +
    scale_fill_viridis_c(option = "turbo", name = "", 
                         limits = c(min(df$air_temp), max(df$air_temp))) + 
    ggtitle(label = "Full") 
  plot(fullPlot)
  
  
  
  # training data visual
  trainPlot <- ggplot(train) + geom_raster(aes(x = lon, y = lat, fill = air_temp)) +
    theme_bw() +
    scale_fill_viridis_c(option = "turbo", name = "", 
                         limits = c(min(df$air_temp), max(df$air_temp))) + 
    ggtitle(label = "Train") 
  plot(trainPlot)
  
  
  
  # test  data visual
  testPlot <- ggplot(test) + geom_raster(aes(x = lon, y = lat, fill = air_temp)) +
    theme_bw() +
    scale_fill_viridis_c(option = "turbo", name = "", 
                         limits = c(min(df$air_temp), max(df$air_temp))) + 
    ggtitle(label = "Test") 
  plot(testPlot)
  
  save(train, test, ind, file = "big_data_analysis/dataframes/simulatedMAR.rda")
}





if (dataCase == "BLOCKS"){
  
  blockNum <- 100
  
  lon_min <- min(df$lon) 
  lon_max <- max(df$lon) 
  lat_min <- min(df$lat) 
  lat_max <- max(df$lat) 
  
  blockSize <- blockNum * 90/1153
  
  #block 1 (bottom left)
  lon_start1 = 15
  lon_end1 <- lon_start1 + blockSize
  
  lat_start1 = 30
  lat_end1 = lat_start1 + blockSize
  
  test1 <- df[df$lon >= lon_start1 & df$lon < lon_end1 & df$lat >= lat_start1 & df$lat < lat_end1, ]
  train <- df[!(df$lon >= lon_start1 & df$lon < lon_end1 & df$lat >= lat_start1 & df$lat < lat_end1), ]
  

  # block 2 (middle)
  lon_start2 = 45
  lon_end2 <- lon_start2 + blockSize
  
  lat_start2 = 80
  lat_end2 = lat_start2 + blockSize
  
  test2 <- rbind(test1, df[df$lon >= lon_start2 & df$lon < lon_end2 & df$lat >= lat_start2 & df$lat < lat_end2, ])
  train <- train[!(train$lon >= lon_start2 & train$lon < lon_end2 & train$lat >= lat_start2 & train$lat < lat_end2), ]
  
  # block 3 (bottom left) finishes test set 
  lon_start = 75
  lon_end <- lon_start + blockSize
  
  lat_start = 45
  lat_end = lat_start + blockSize
  
  test <- rbind(test2, df[df$lon >= lon_start & df$lon < lon_end & df$lat >= lat_start & df$lat < lat_end, ])
  train <- train[!(train$lon >= lon_start & train$lon < lon_end & train$lat >= lat_start & train$lat < lat_end), ]
  ind <- as.numeric(row.names(test))
  
  
  
  # full data visual
  fullPlot <- ggplot(df) + geom_raster(aes(x = lon, y = lat, fill = air_temp)) +
    theme_bw() +
    scale_fill_viridis_c(option = "turbo", name = "", 
                         limits = c(min(df$air_temp), max(df$air_temp))) + 
    ggtitle(label = "Full") 
  plot(fullPlot)
  
  
  
  # train data visual
  trainPlot <- ggplot(train) + geom_raster(aes(x = lon, y = lat, fill = air_temp)) +
    theme_bw() +
    scale_fill_viridis_c(option = "turbo", name = "", 
                         limits = c(min(df$air_temp), max(df$air_temp))) + 
    ggtitle(label = "Train") 
  plot(trainPlot)
  
  
  
  # test data visual 
  dfCopy <- df
  dfCopy$testBlockValue <- NA
  dfCopy[ind,4] <- test[,3]
  
  testPlot <- ggplot(dfCopy) + geom_raster(aes(x = lon, y = lat, fill = testBlockValue)) +
    theme_bw() +
    scale_fill_viridis_c(option = "turbo", na.value = "white", 
                         limits = c(min(df$air_temp), max(df$air_temp)), 
                         name = "") + 
    ggtitle(label = "Test") 
  
  plot(testPlot)
  
  
  save(train, test, ind, 
       file = "big_data_analysis/dataframes/simulatedBLOCKS.rda")
  
}

```

Okay, now let's write out our possibilities for the normalization cases: 

```{r}

switch(normalizeCase,
  "none" = {
    normChoice <- FALSE
  },
  "exact" = {
    normChoice <- TRUE
    normMethod <- "exact"
  },
  "kronecker" = {
    normChoice <- TRUE
    normMethod <- "exactKronecker"
  },
  "fft" = {
    normChoice <- TRUE
    normMethod <- "both"
  }
)

```


Setting up the params, x, y, covariates, and the LKinfo object. 

```{r}
#training 
#locations
x <- cbind(train$lat, train$lon)
#response air temp
y <- train$air_temp
#predictors (none in this case)
#Z <- cbind(train$elevation, train$ghi)

#sanity check
length(unique(x[,1]))
length(unique(x[,2]))


#testing
#locations
xtest <- cbind(test$lat, test$lon)
#response air temp
ytest <- test$air_temp
#predictors
#Ztest <- cbind(test$elevation, test$ghi)


# setup params

# there is no "normalizeMethod" selection for none
if (normalizeCase == "none"){
  LKinfo <- LKrigSetup(x, NC = 25, nlevel = 4, NC.buffer = 10, 
                       normalize = normChoice, 
                       nu = 1, a.wght = 4.015)
} else{
  LKinfo <- LKrigSetup(x, NC = 25, nlevel = 4, NC.buffer = 10, 
                       normalize = normChoice, normalizeMethod = normMethod,
                       nu = 1, a.wght = 4.015)
}
```

Fitting:

```{r}
comp.time.fit <- system.time(fit <- LatticeKrig(x, y, LKinfo = LKinfo, verbose = FALSE))
```

Predicting the whole surface (not just at unknown locations)

```{r}
predgrid <- make.surface.grid(grid)
comp.time.pred <- system.time(preds <- predict(fit, predgrid))
```

Let's take a look at our predicted surface: 

```{r}
summary(abs(preds - air_temp))
summary(abs(preds[ind] - ytest))

dfPred <- data.frame(lat = df$lat, lon = df$lon, air_temp = preds)

# predicted data visual
  predPlot <- ggplot(dfPred) + geom_raster(aes(x = lon, y = lat, fill = air_temp)) +
    theme_bw() +
    scale_fill_viridis_c(option = "turbo", name = "") + 
    ggtitle(label = "Predicted Surface (Blocks)") 
plot(predPlot)


```


Building in the option to do conditional simulation to find the SE: 

```{r}
if (conditionalSim == TRUE){
  
  # conditional simulation to determine prediction SE
  comp.time.sim <- system.time(outputSim <- LKrig.sim.conditional(fit,
                                      x.grid = xtest,
                                      M = numDraws))
  
  #prediction SE needs to include uncertainty due to nugget 
  comp.time.SE <- system.time(standardError<- sqrt( 
        apply( outputSim$g.draw, 1, "var") +
        fit$sigma.MLE^2))
}
```

Total times and saving results: 

```{r}
# total time
if (conditionalSim == TRUE){
  comp.time.total <- comp.time.fit + comp.time.pred + comp.time.sim + comp.time.SE
  
  results <- list(y = ytest, #true values 
                predSurface = preds, #predicted surface
                SE = standardError, #SE
                time = comp.time.total) #total time
  
} else{
  comp.time.total <- comp.time.fit + comp.time.pred
  
  results <- list(y = ytest, #true values 
                predSurface = preds, #predicted surface
                time = comp.time.total) #total time
}

save( results, fit, comp.time.total, 
      file=paste0("big_data_analysis/results/",normalizeCase,dataCase,"Results.rda") )
```



